Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-06 manuscript.tex
edited sec 4.1 - 1

To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial facula
%\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase equals to 0. Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\% \citep[e.g.][]{Borgniet-2015}. In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is different from the two others with a maximum amplitude happening at a different phase.

@@

Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively. Concerning the correlations between the different RV estimates and the different CCF width parameters, there is a stronger correlation between SN FWHM and SN mean RV ($R=0.98$) respect to the one between FWHM and N mean RV ($R=0.84$). In this case the correlation between SN FWHM and SN median RV is the weakest, with $R=0.50$. This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters. Therefore, the SN parameters may better probe stellar activity. We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.

>>>>

To see the impact of a facula on the parameters of different models of the CCF, we simulated the effect of an equatorial facula
%\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase equals to 0. 
Note that a 3\% faculae is relatively large for the Sun; at maximum activity, large faculae generally have a size of 1\% \citep[e.g.][]{Borgniet-2015}. 
In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is notably different from the two others with a maximum amplitude happening at a different phase.

@@

Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively. 
%
There is a stronger correlation between SN FWHM and SN mean RV ($R=0.98$) than between FWHM and N mean RV ($R=0.84$), but the correlation between SN FWHM and SN median RV is the weakest ($R=0.50$). 
This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters. Therefore, the SN parameters may better probe stellar activity. 
We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
